\section{Conclusion}
This document is used to describe the actions taken to complete the SCORE 2021 AI4Agile prompt on the Jira Cloud platform by building a plugin using the interface and development tools that the parent company, Atlassian, provided. The new plugin performed epic decomposition, story optimization, task generation, and relationship visualization for various forms of user stories. To implement these new features on Jira Cloud, research was done on how Jira Cloud worked, and how the AI components should function and interface with Jira. Determining the best area to implement the new features was important, because the team wanted somewhere the user frequently visits and which can be seen easily. Section 6 of this paper went into detail on the specific area chosen and its reasoning. 

The team for this project consisted of 7 people, including mentors and advisors, where only the faculty advisor had previous knowledge of AI, therefore the rest of the team members had a steep learning curve. Due to the wide range of AI types, research needed to be done to determine the best AI type for each component. The specific AI type for epic decomposition uses K-means clustering, while story optimization uses a combination of word embedding, feature extraction, and cosine similarity. For task generation, part-of-speech tagging and sentence classification were used. Section 6 explained the implementation details of these components, while section 5 went into the rationale behind the sub-components used. In the end, connecting the backend processes into Jira Cloud required learning to use another set of tools, namely Flask and jQuery AJAX, which were also mentioned in section 6. 

Overall, the AI and UI components performed well, but could be improved. For example, task generation results would not always be complete sentences, creating a need for editing the suggestions before use. This potential for improvement is where the future works in section 9 come in, as they fall into the plans for the next phase of development.