\documentclass[11pt,journal,onecolumn]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage[textwidth = 155mm]{geometry}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\setlist[itemize]{align=parleft, left=0pt..1em}
\begin{document}

\title{Team Katara - AI4Agile Initial Report}

\author{
    \IEEEauthorblockN{Phong Bach\IEEEauthorrefmark{0}, Emily Cawlfield\IEEEauthorrefmark{0}, Nain Galvan\IEEEauthorrefmark{0}, Aric Monary\IEEEauthorrefmark{0}\\}
    \IEEEauthorblockA{\IEEEauthorrefmark{0}Washington State University Everett}
}

\maketitle

\let\clearpage\relax
\include{./01.introduction}
\include{./02.preliminaryUnderstanding}
\include{./03.collaboration}
\include{./04.requirements}
\include{./05.design}
\include{./06.implementation}
\include{./07.demonstration}
\include{./08.verificationAndValidation}
\include{./09.futureWorks}
\include{./10.conclusion}

\section*{Acknowledgment}

Special thanks to Dr. Bolong Zeng, Skip Baccus, and Jeremy Thompson for their support, assistance, and time given to the team and this project.

\begin{thebibliography}{00} 
\bibitem{b1} Hoa Khanh Dam, Truyen Tran, John Grundy, Aditya Ghose and Yasutaka Kamei, Towards effective AI-powered agile project management, Proceedings of the 41st International Conference on Software Engineering (ICSE 2019), New Ideas and Emerging Results.
\bibitem{b2} R, Luis, Guzman, Jaime, A, Sebastián. (2015). Extraction of goals and their classification in the KAOS model using natural language processing. Ingeniare. Revista chilena de ingeniería. 23. 59-66. 10.4067/S0718-33052015000100007.
\bibitem{b3} Das, Bidyut, Majumder, Mukta, Phadikar, Santanu. (2018). A Novel System for Generating Simple Sentences from Complex and Compound Sentences. International Journal of Modern Education and Computer Science. 1. 57-64. 10.5815/ijmecs.2018.01.06.
\end{thebibliography}

\end{document}
