\section{Introduction}
AI4Agile is an add-on application built for Jira Software Cloud \cite{jira2}, made to assist software development teams in agile environments in streamlining user story refinement. The application utilizes Artificial Intelligence (AI) to power processes that refine user stories from epics into tasks. It offers AI-based smart suggestions of requirement work items with different levels of details: epics, user stories, and tasks. Finally, the application provides an integrated tool that allows users to visualize the explicit and implicit relationships among the requirements. Team Katara from Washington State University, Everett, WA USA submits this report for the ICSE SCORE 2021 competition. 

The rest of the report is organized as follows. Section \ref{background} outlines preliminary background information of the app, the stakeholders, and the team's development process. Section \ref{requirement} summarizes the requirements modeling, goal-oriented acquistion and decomposition. Section \ref{design} outlines the design of the tool by highlighting our decision making process. Section \ref{implementation} expands on detailed changes made transitioning from initial design to the final implementation, and covers our effort in deploying the app on the cloud. Section \ref{demo} provides walkthroughs of two user stories to demonstrate our tool's primary functionalities, and a brief summary of our work done for testing. Interested readers may find instructions on trying out the app and its source code in \ref{instructions}. Lastly, Section \ref{conclusion} reflects on the outcome of the project and explores its potential future prospects. 
