\section{Future Works and Conclusion}
\label{conclusion}
As part of an academic capstone project, regardless of whether the team would advance into the next stage with the SCORE competition, we plan to continue with the project for the next few months. The team have noticed several possible improvements needed for our main features. For instance, in the epic decomposition process, we might implement dynamic clustering of stories, that automatically adjust the numbers of stories generated, instead of relying on user provided parameters. The main improvement for story optimization would be in optimizing the algorithm to be faster, as the current wait time is relatively long compared to our goal, as it caused a noticeable delay. The relationship visualization component also has multiple adjustments that could be made, such as filtering and ease-of-use controls for zooming and panning. 

In conclusion, the team has completed the tasks within the scope as we defined based upon the AI4Agile project proposal. In this paper, we presented the team's structure and SE process, as well as all major stakeholders involved. We then described in details the lifecycle throughout the project, covering requirements, design, implementation and final user story-based testing and demonstration. The team have plans to continue the project in the near future as part of our capstone project and will look into exploring several directions where improvements on the main features could be done. As a matter of fact, we have already successfully switched to the Stanza Natural Language Processing (SNLP) \cite{NLP1, stanza} package to improve the results of task generation, which was one of stated goals in our initial submitted report. 

While the team has successfully deployed the prototype on our own for trial usage and testing, our ultimate goal is to publish the project to the Atlassian Marketplace, allowing us to collect feedback from potential real customers, and guide our further improvements.  Overall, not only has the team gained invaluable experience  in various techniques such as AI, NLP and cloud platform deployment, we have also learnt a great deal in applying Software Engineering principles in practice to complete this project. 